Computational Fuzzy Extractors

### 2013-09-04 CompFuzzExt-asiacrypt.tex
Asiacrypt version

%\documentclass[11pt]{article}
\documentclass{llncs}
\def\shownotes{1}

@@

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{assumption}[theorem]{Assumption}
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{problem}[theorem]{Problem}
\newtheorem{construction}{Construction}
%\spn@wtheorem{lemma}{Lemma}{\bfseries}{\itshape}

\newcounter{ctr}
\newcounter{savectr}
\newcounter{ectr}
%
%\newenvironment{newitemize}{%
%\begin{list}{\mbox{}\hspace{5pt}$\bullet$\hfill}{\labelwidth=15pt%
%\labelsep=5pt \leftmargin=20pt \topsep=3pt%
%\setlength{\listparindent}{\saveparindent}%
%\setlength{\parsep}{\saveparskip}%
%\setlength{\itemsep}{3pt} }}{\end{list}}
%
%
%\newenvironment{newenum}{%
%\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=17pt%
%\labelsep=5pt \leftmargin=22pt \topsep=3pt%
%\setlength{\listparindent}{\saveparindent}%
%\setlength{\parsep}{\saveparskip}%
%\setlength{\itemsep}{2pt} }}{\end{list}}
%
%\newenvironment{tiret}{%
%\begin{list}{\hspace{2pt}\rule[0.5ex]{6pt}{1pt}\hfill}{\labelwidth=15pt%
%\labelsep=3pt \leftmargin=22pt \topsep=3pt%
%\setlength{\listparindent}{\saveparindent}%
%\setlength{\parsep}{\saveparskip}%
%\setlength{\itemsep}{2pt}}}{\end{list}}
%
%
%\newenvironment{blocklist}{\begin{list}{}{\labelwidth=0pt%
%\labelsep=0pt \leftmargin=0pt \topsep=10pt%
%\setlength{\listparindent}{\saveparindent}%
%\setlength{\parsep}{\saveparskip}%
%\setlength{\itemsep}{20pt}}}{\end{list}}
%
%\newenvironment{blocklistindented}{\begin{list}{}{\labelwidth=0pt%
%\labelsep=30pt \leftmargin=30pt\topsep=5pt%
%\setlength{\listparindent}{\saveparindent}%
%\setlength{\parsep}{\saveparskip}%
%\setlength{\itemsep}{10pt}}}{\end{list}}
%
%\newenvironment{onelist}{%
%\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=18pt%
%\labelsep=7pt \leftmargin=25pt \topsep=2pt%
%\setlength{\listparindent}{\saveparindent}%
%\setlength{\parsep}{\saveparskip}%
%\setlength{\itemsep}{2pt} }}{\end{list}}
%
%\newenvironment{twolist}{%
%\begin{list}{{\rm (\arabic{ctr}.\arabic{ectr})}%
%\hfill}{\usecounter{ectr} \labelwidth=26pt%
%\labelsep=7pt \leftmargin=33pt \topsep=2pt%
%\setlength{\listparindent}{\saveparindent}%
%\setlength{\parsep}{\saveparskip}%
%\setlength{\itemsep}{2pt} }}{\end{list}}
%
%\newenvironment{centerlist}{%
%\begin{list}{\mbox{}}{\labelwidth=0pt%
%\labelsep=0pt \leftmargin=0pt \topsep=10pt%
%\setlength{\listparindent}{\saveparindent}%
%\setlength{\parsep}{\saveparskip}%
%\setlength{\itemsep}{10pt} }}{\end{list}}
%
%\newenvironment{newcenter}[1]{\begin{centerlist}\centering%
%\item #1}{\end{centerlist}}
%
%\newenvironment{codecenter}[1]{\begin{small}\begin{centerlist}\centering%
%\item #1}{\end{centerlist}\end{small}}

@@

\title{\textbf{Computational Fuzzy Extractors}}
\author{Benjamin Fuller\inst{1} \and Xianrui Meng\inst{2} \and Leonid Reyzin\inst{2}}
\authorrunning{B. Fuller \and X. Meng \and L. Reyzin}
\institute{Boston University and MIT Lincoln Laboratory \and Boston University} 
\tocauthor{Benjamin Fuller, Xianrui Meng, and Leonid Reyzin (Boston University)}

@@

 Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
Let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$, where $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.  If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.  (A recent result of Brakerski et al.~\cite{brakerski2013classical} shows security of $\LWE$ based on hardness of approximating lattices problems for classical algorithms.  We have not considered how this result can be integrated into our analysis.)

>>>>

%\documentclass[11pt]{article}
\documentclass{llncs}
\def\shownotes{0}

@@

\newtheorem{construction}{Construction}

@@

\title{Computational Fuzzy Extractors}
\author{Benjamin Fuller\inst{1} \and Xianrui Meng\inst{2} \and Leonid Reyzin\inst{2}}
\authorrunning{B. Fuller \and X. Meng \and L. Reyzin}
\institute{Boston University and MIT Lincoln Laboratory \and Boston University} 
\tocauthor{Benjamin Fuller, Xianrui Meng, and Leonid Reyzin (Boston University)}

@@

 Regev~\cite{regev2005LWE} and Peikert~\cite{peikert2009latticereduction} show that $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure when the distribution $\chi$ of errors is Gaussian, as follows.
Let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$, where $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.  If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \bar{\Psi}_\rho^m}$ is secure.  (A recent result of Brakerski et al.~\cite{brakerski2013classical} shows security of $\LWE$ based on hardness of approximating lattices problems for classical algorithms.  We have not considered how this result can be integrated into our analysis.)
